Building Sustainable Software - The CSDMS Approach

### 2014-07-14 paper.tex
Added CU to affiliation.
Moved WMT screenshot figure into WMT section.

\thanks{{}$^{\dag}$ Community Surface Dynamics Modeling System, Boulder, CO}

@@

The \csdms{} Web Modeling Tool\footnote{https://csdms.colorado.edu/wmt}
(\wmt{}) is a web
application that provides an Ajax client-side (the \wmt{}
client\footnote{https://github.com/csdms/wmt-client}) graphical interface
(figure~\ref{fig:wmt_screenshot}) and a RESTful
server-side database and API (the \wmt{} server\footnote{https://github.com/csdms/wmt}) that allows users to build and run coupled Earth system models on
a high-performance computing cluster from a web browser. \wmt{} was designed
with four objectives:
\begin{itemize}

@@

\begin{comment}
\subsection{Software sustainability through expanded functionality}

@@

\begin{figure}
  \caption{The \csdms Web Modeling Tool}
  \begin{center}
    \includegraphics[scale=.25]{wmt.eps}
  \end{center}
  \label{fig:wmt_screenshot}
\end{figure}

>>>>

\thanks{{}$^{\dag}$Community Surface Dynamics Modeling System, University of
Colorado}

@@

The \csdms{} Web Modeling Tool\footnote{https://csdms.colorado.edu/wmt}
(\wmt{}) is a web
application that provides an Ajax client-side (the \wmt{}
client\footnote{https://github.com/csdms/wmt-client}) graphical interface
(Figure~\ref{fig:wmt_screenshot}) and a RESTful
server-side database and API (the \wmt{} server\footnote{https://github.com/csdms/wmt}) that allows users to build and run coupled Earth system models on
a high-performance computing cluster from a web browser. \wmt{} was designed
with four objectives:
\begin{itemize}

@@

\begin{figure}
  \caption{The \csdms{} Web Modeling Tool}
  \begin{center}
    \includegraphics[scale=.25]{wmt.eps}
  \end{center}
  \label{fig:wmt_screenshot}
\end{figure}
\begin{comment}
\subsection{Software sustainability through expanded functionality}

@@
